Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-02-22 apples_and_oranges.qmd
Clinical sample

# F. Estimate Means and CIs for the overall sample using baseline percentage variable ----------------------------------

>>>>

# F Clinical Levels Depression Sensitivity Analysis ---------------------------------------

# We need to decide how we want to do this. We have mdd, mood, sub, and cut categories. For now I'll just exclude sub.

# test <- df_appl_v_orange %>%
#   filter(psy_or_med == 1) %>%
#   distinct(new_study_id, .keep_all = TRUE)
# 
# summary_test <- test %>%
#   group_by(diagnosis) %>%
#   summarise(count = n())

#take study ids where sample has clinical levels of depression
clin_study_ids <-
  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id

# use those ids to subset all dataframes in the list
list_clin_study <- list()

  list_clin_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
                                                          %in% clin_study_ids,]

# count the number of studies
study_count_clin_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% clin_study_ids,])
# CB checked, correct.

# apply the metareg function to the list of clinical studies
model_1 <- as.formula(~ four_level_var)
list_model_1_clin_study <- run_metaregression(list_clin_study , model_1)

# extract coefficients and model characteristics.
condition <- levels(list_df_simulated[[1]]$four_level_var)
aggregate_results_clin_study <-  aggregate_model_results(list_model_1_clin_study, condition)

# extract SMDs from the list for clinical studies
means_clin_study <-  lapply(list_model_1_clin_study, extract_coefficients_func)

# calculate mean SMDs and ses
condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
coef_and_se_means_clin_study <- calculate_mean_coefs_ses(means_clin_study, condition)
coef_and_se_means_clin_study <- data.frame(cbind(condition, coef_and_se_means_clin_study))

# add the ns to the dataframe
coef_and_se_means_clin_study$n  <- study_count_clin_study[study_count_clin_study$is_missing ==F,]$n

# G. Estimate Means and CIs for the overall sample using baseline percentage variable ----------------------------------
